### 2021-10-06 arxiv-draft/sections/appendix.tex
arxiv draft

>>>>

Figure~\ref{fig:lissyl2} shows how traders interact with \cm on Arbitrum. First, a trader sends a \texttt{depositETH} transaction on Ethereum to the Inbox contract to deposit \textit{X} amount of ETH to the Arbitrum chain. Once the transaction is confirmed, \textit{X} amount of ETH will be credited to the trader's address on the Arbitrum chain. Trader can now interact with \cm and execute its functions by sending the instruction and data required for those executions to either (1) the Arbitrum regular Inbox on Ethereum, or (2) the sequencer. In our example, trader uses the regular Inbox to execute \texttt{depositEther()} and the sequencer to execute \texttt{submitBid()} from \cm that lives entirely on Arbitrum chain. 
Accordingly, trader deposits ETH to \cm smart contract by sending the instruction and data for executing the \texttt{depositEther()} to the Arbitrum Inbox contract that lives on Ethereum. A validator fetches this transaction from the Inbox, executes it, and asserts the result to ArbOS. Next, trader sends the instruction and data for execution of \texttt{submitBid()} to the sequencer. The sequencer then inserts this message into the Inbox that it owns. This Inbox contract has the same interface as the regular Inbox contract, however, it is \textit{owned} by the sequencer. A validator sees the transaction in the sequencer Inbox of the bridge, executes it,  and asserts the result to ArbOS. Periodically, the entire state of ArbOS is committed back to Ethereum.

### 2021-10-06 arxiv-draft/sections/paper.tex
arxiv draft

For our experiments and measurements, we implement a call market from scratch. \cm will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq}). Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). \cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg we implement 5 variants, each around 300 SLOC). We tested it with the Mocha testing framework using Truffle~\cite{TruffleO71:online} on Ganache-CLI~\cite{GanacheT25:online} to obtain our performance metrics. Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored. The Solidity source code for \cm and Truffle test files are available in a GitHub repository.\footnote{Github: Link removed for anonymity.} We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}. We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} and it only fails some `informational' warnings that are intentional design choices (\eg a costly loop). All measurements assume a block gas limit of $11\,741\,495$ and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Table~\ref{tab:cm_functions} summarizes \cm's primary operations.\

@@

>>>>

For our experiments and measurements, we implement a call market from scratch. \cm will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq}). Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). \cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg we implement 5 variants, each around 300 SLOC). We tested it with the Mocha testing framework using Truffle~\cite{TruffleO71:online} on Ganache-CLI~\cite{GanacheT25:online} to obtain our performance metrics. Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored. The Solidity source code for \cm and Truffle test files are available in a GitHub repository.\footnote{https://github.com/MadibaGroup/2020-Orderbook} We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}. We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} and it only fails some `informational' warnings that are intentional design choices (\eg a costly loop). All measurements assume a block gas limit of $11\,741\,495$ and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Table~\ref{tab:cm_functions} summarizes \cm's primary operations.\

@@

\subsubsection*{Acknowledgements.}  The authors thank the AMF (Autorité des Marchés Financiers) for supporting this research project. J. Clark also acknowledges partial funding from the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant. M. Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).

### 2021-10-06 arxiv-draft/tables/frontrunning.tex
arxiv draft

\begin{table*}[t]

\centering
\tiny
%\resizebox{1.7\columnwidth}{!}{

@@

\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\headrowfrontTwo{\shortstack{Centralized Continuous\\ Market (Coinbase)}} &
\headrowfrontTwo{\shortstack{Partially Off-chain Continuous\\ Market (EtherDelta)}} & 
\headrowfrontTwo{\shortstack{Partially Off-chain Continuous \\Market w/ Roll-up (Loopring)}} & 
\headrowfrontTwo{\shortstack{On-chain Continuous \\Market (OasisDex)}}  &
\headrowfrontTwo{\shortstack{On-chain Dark \\Continuous Market (TEX)}} &
\headrowfrontTwo{\shortstack{On-chain Automated \\Market Maker (Uniswap)}}  & 
\headrowfrontTwo{\shortstack{On-chain Call Market \\w/ Price Improvement}} &
\headrowfrontTwo{\shortstack{On-chain Call Market (\cm)}}  & 
\headrowfrontTwo{\shortstack{On-chain Call Market  \\w/ Roll-up (\cm variant)}}  &
\headrowfrontTwo{\shortstack{On-chain Dark \\Call Market (Galal \etal)}}
\\

@@

\caption{\footnotesize{An evaluation of front-running attacks (rows) for different types of order books (columns). Front-running attacks are in three categories: \underline{Ins}ertion, \underline{disp}lacement, and \underline{supp}ression. A full dot (\tinyfull) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\tinyprt) is awarded when the front-running attack is possible but expensive, and we give no award (\tinyempt) if the attack is feasible}. 
\label{tab:front}}
\end{table*}

>>>>

%\begin{adjustbox}{center} %horizontal display
\begin{landscape} %vertical display
\begin{table}[t]
\setlength{\tabcolsep}{3\tabcolsep}
\centering

\footnotesize

@@

\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\headrowfront{\scriptsize{Centralized Continuous Market (Coinbase)}} &
\headrowfront{\scriptsize{Partially Off-chain Continuous Market (EtherDelta)} } & 
\headrowfront{\scriptsize{Partially Off-chain Continuous Market w/ Roll-up (Loopring)} } & 
\headrowfront{\scriptsize{On-chain Continuous Market (OasisDex)} } &
\headrowfront{\scriptsize{On-chain Dark Continuous Market (TEX)} }&
\headrowfront{\scriptsize{On-chain Automated Market Maker (Uniswap)} } & 
\headrowfront{\scriptsize{On-chain Call Market w/ Price Improvement}} &
\headrowfront{\scriptsize{On-chain Call Market (\cm)}}  & 
\headrowfront{\scriptsize{On-chain Call Market w/ Roll-up (\cm variant)}}  &
\headrowfront{\scriptsize{On-chain Dark Call Market (Galal \etal)}} 
\\

@@

%\end{adjustbox}

\caption{An evaluation of front-running attacks (rows) for different types of order books (columns). Front-running attacks are in three categories: \underline{Ins}ertion, \underline{disp}lacement, and \underline{supp}ression. A full dot (\full) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\prt) is awarded when the front-running attack is possible but expensive, and we give no award (\empt) if the attack is feasible. 
\label{tab:front}}
\end{table}

\end{landscape}

### 2021-10-06 arxiv-draft/tables/frontrunning2.tex
arxiv draft

\centering
\tiny
%\resizebox{1.7\columnwidth}{!}{

@@

\caption{\footnotesize{An evaluation of front-running attacks (rows) for different types of order books (columns). Front-running attacks are in three categories: \underline{Ins}ertion, \underline{disp}lacement, and \underline{supp}ression. A full dot (\tinyfull) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\tinyprt) is awarded when the front-running attack is possible but expensive, and we give no award (\tinyempt) if the attack is feasible}. 
\label{tab:front}}
\end{table*}

>>>>

\centering
%\tiny %commented for the arxiv version
%\resizebox{1.7\columnwidth}{!}{

@@

\caption{An evaluation of front-running attacks (rows) for different types of order books (columns). Front-running attacks are in three categories: \underline{Ins}ertion, \underline{disp}lacement, and \underline{supp}ression. A full dot (\full) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\prt) is awarded when the front-running attack is possible but expensive, and we give no award (\empt) if the attack is feasible. 
\label{tab:front}}
\end{table*}
